Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-04-02 main.Rmd
quasi-circular diagram and caption update

```{r quasi-circular-example, echo = FALSE, out.width = "100%",fig.cap="The time domain distributed as linear granularities $B$ (bottom granularity), $G'$, $H'$ and quasi-circular granularities $Q(B, G')$ and $Q(B, H')$. Both $Q(B, G')$ and $Q(B, H')$ have repeating patterns unlike $G'$ or $H'$ and the patterns are guided by the distribution of $B$ within $G'$ and $H'$ and remains constant within a period shown by the hashed arrows."}
knitr::include_graphics("Figs/quasi-circular-ex.png")
```

@@

```{r aperiodic-example, echo=FALSE,out.width = "100%",fig.cap="Terminology and intuition of aperiodic cyclic granularities are shown. Panel a shows the time domain distributed as linear granularities Day, Semester, Semester Week, within semester breaks, in-session and aperiodic cyclic granularity Week-of-semester. $A(B, M)$ consists of three categories, 1, 2 and 0 corresponding to within semester breaks, in-session and non-semester period respectively. Panel b depicts the intuition through a measuring tape analogy which needs to be folded at different points every year since $M1$ and $M2$ will fall in different weeks."}
knitr::include_graphics("Figs/aperiodic-ex2.png")
```

>>>>

```{r quasi-circular-example, echo = FALSE, out.width = "100%",fig.cap="
Terminology and intuition of quasi-circular granularities are shown. Panel a shows the time domain distributed as linear granularities $B$ (bottom granularity), $G$, $H'$ and quasi-circular granularities $Q(B, G)$ and $Q(B, H')$. Both $Q(B, G)$ and $Q(B, H')$ have repeating patterns unlike $G$ or $H'$ and the patterns are guided by the distribution of $B$ within $G$ and $H'$ and remains constant within a period shown by the hashed arrows. Panel b depicts the intuition through a measuring tape analogy where the folds are not of same length but has same length over a period."}
knitr::include_graphics("Figs/quasi-circular-ex2.png")
```

@@

```{r aperiodic-example, echo=FALSE,out.width = "100%",fig.cap="Terminology and intuition of aperiodic cyclic granularities are shown. Panel a shows the time domain distributed as linear granularities Day, Semester, within semester breaks, in-session and aperiodic cyclic granularity Week-of-Semester. $A(B, M)$ consists of three categories 0, 1, 2 non-semester period, within-semester breaks and in-session semester period respectively. Panel b depicts the intuition through a measuring tape analogy which needs to be folded at different points every year since $M1$ and $M2$ will fall in different weeks."}
knitr::include_graphics("Figs/aperiodic-ex2.png")
```
